### 2025-06-18 simulation.qmd
20250618 - headings for organization

@@

@@

@@

@@

@@

bootstrappedFantasyPoints_summary <- bootstrappedFantasyPoints %>% 
  group_by(id) %>% 
  summarise(
    mean = mean(projectedPoints, na.rm = TRUE),
    SD = sd(projectedPoints, na.rm = TRUE),
    ceiling = quantile(projectedPoints, .90), # 90th quantile
    min = min(projectedPoints, na.rm = TRUE),
    max = max(projectedPoints, na.rm = TRUE),
    range = max(projectedPoints, na.rm = TRUE) - min(projectedPoints, na.rm = TRUE),
    IQR = IQR(projectedPoints, na.rm = TRUE),
    MAD = mad(projectedPoints, na.rm = TRUE),
    CV = SD/mean,
    median = median(projectedPoints, na.rm = TRUE),
    pseudomedian = DescTools::HodgesLehmann(projectedPoints, na.rm = TRUE),
    mode = petersenlab::Mode(projectedPoints, multipleModes = "mean"),
    skewness = psych::skew(projectedPoints, na.rm = TRUE),
    kurtosis = psych::kurtosi(projectedPoints, na.rm = TRUE)
  )
```

@@

@@

>>>>

#### Prepare Data {#sec-simulationProjectedPointsBootstrappingPrepareData}

@@

#### Bootstrapping Function {#sec-simulationProjectedPointsBootstrappingFunction}

@@

#### Run the Bootsrapping Simulation {#sec-simulationProjectedPointsBootstrappingRun}

@@

#### Score Fantasy Points from the Simulation {#sec-simulationProjectedPointsBootstrappingScore}

@@

#### Summarize Players' Distribution of Projected Fantasy Points {#sec-simulationProjectedPointsBootstrappingSummarize}

@@

bootstrappedFantasyPoints_summary <- bootstrappedFantasyPoints %>% 
  group_by(id) %>% 
  summarise(
    mean = mean(projectedPoints, na.rm = TRUE),
    SD = sd(projectedPoints, na.rm = TRUE),
    q10 = quantile(projectedPoints, .10), # 10th quantile
    q90 = quantile(projectedPoints, .90), # 90th quantile
    min = min(projectedPoints, na.rm = TRUE),
    max = max(projectedPoints, na.rm = TRUE),
    range = max(projectedPoints, na.rm = TRUE) - min(projectedPoints, na.rm = TRUE),
    IQR = IQR(projectedPoints, na.rm = TRUE),
    MAD = mad(projectedPoints, na.rm = TRUE),
    CV = SD/mean,
    median = median(projectedPoints, na.rm = TRUE),
    pseudomedian = DescTools::HodgesLehmann(projectedPoints, na.rm = TRUE),
    mode = petersenlab::Mode(projectedPoints, multipleModes = "mean"),
    skewness = psych::skew(projectedPoints, na.rm = TRUE),
    kurtosis = psych::kurtosi(projectedPoints, na.rm = TRUE)
  )
```

@@

#### View Players' Distribution of Projected Fantasy Points {#sec-simulationProjectedPointsBootstrappingView}

@@

#### `SimDesign` Package {#sec-simulationProjectedPointsMonteCarloSimDesign}
